---
title: "Telecom Customer Churn Analysis"
output: pdf_document
---
1. Data Preparation.
```{r}
rm(list=ls())
library(readxl)
library(Hmisc)
library(MASS)
library(caret)
library(regclass)
library(ISLR)
library(boot)
library(vcd)
library(pROC)
library (ROCR)
data<-na.omit(read.csv("~/Desktop/HW/401/final project/WA_Fn-UseC_-Telco-Customer-Churn.csv"))
```
1) Variable Transformation.
```{r}
data$gender<-ifelse(data$gender=='Female',1,0)
data$Partner<-ifelse(data$Partner=='Yes',1,0)
data$Dependents<-ifelse(data$Dependents=='Yes',1,0)
data$PhoneService<-ifelse(data$PhoneService=='Yes',1,0)
data$PaperlessBilling<-ifelse(data$PaperlessBilling=='Yes',1,0)
data$Churn<-ifelse(data$Churn=='Yes',1,0)
data$MultipleLines<-ifelse(data$MultipleLines=='Yes',1,0)
data$OnlineSecurity<-ifelse(data$OnlineSecurity=='Yes',1,0)
data$OnlineBackup<-ifelse(data$OnlineBackup=='Yes',1,0)
data$DeviceProtection<-ifelse(data$DeviceProtection=='Yes',1,0)
data$TechSupport<-ifelse(data$TechSupport=='Yes',1,0)
data$StreamingTV<-ifelse(data$StreamingTV=='Yes',1,0)
data$StreamingMovies<-ifelse(data$StreamingMovies=='Yes',1,0)
data$EC<-ifelse(data$PaymentMethod=='Electronic check',1,0)
data$MC<-ifelse(data$PaymentMethod=='Mailed check',1,0)
data$BT<-ifelse(data$PaymentMethod=='Bank transfer (automatic)',1,0)
data$CC<-ifelse(data$PaymentMethod=='Credit card (automatic)',1,0 )
data$mtm<-ifelse(data$Contract=='Month-to-month',1,0)
data$oy<-ifelse(data$Contract=='One year',1,0)
data$ty<-ifelse(data$Contract=='Two year',1,0)
data$DSL<-ifelse(data$InternetService=='DSL',1,0)
data$FO<-ifelse(data$InternetService=='Fiber optic',1,0)
```
2) Clean Data.
```{r}
clean<-data[c(1,2,3,4,5,6,7,8,10,11,12,13,14,15,17,19,20,21,22,23,24,25,26,27,28,29,30)]
```
2. Feature Selection & Engineering.
```{r}
library(reshape2)
cormat<-cor(clean[2:27])
melted_cormat <- melt(cormat)
library(ggplot2)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
```
For reliable interpretation of explanatory variables, Total Charge, Credit Card Payment dummy, Two Year Contract dummy and  Fiber Optic dummy variables are excluded from the model.
3. Logistic Regression.
1). No train-test split.
```{r}
churn_logit<-glm(Churn~ gender+SeniorCitizen+Partner+Dependents+tenure+PhoneService+MultipleLines+OnlineSecurity+OnlineBackup+
                   DeviceProtection+TechSupport+StreamingTV+StreamingMovies+PaperlessBilling+
                   MonthlyCharges+EC+MC+BT+mtm+oy+DSL+StreamingTV:StreamingMovies,data=clean,family=binomial(link="logit"))
summary(churn_logit) 
car::vif(churn_logit)
preddata<-with(clean,data.frame(customerID,gender,SeniorCitizen,Partner,Dependents,tenure,PhoneService,MultipleLines,OnlineSecurity,OnlineBackup,DeviceProtection,TechSupport,StreamingTV, StreamingMovies, PaperlessBilling, MonthlyCharges, TotalCharges, Churn, EC,MC,BT,CC,mtm,oy,ty,DSL,FO))
probchurn<-predict(churn_logit,newdata=preddata,type="response")
preddefault<-ifelse(probchurn > 0.5, 1,0)
clean$probchurn<-probchurn
confusionMatrix(data = as.factor(preddefault),reference = as.factor(clean$Churn),positive = "1")
roc(clean$Churn,churn_logit$fitted.values, plot=TRUE)
par(pty="s")
roc(clean$Churn,churn_logit$fitted.values, plot=TRUE, legacy.axes=TRUE, percent=TRUE, xlab="FP Rate", ylab="TP Rate",print.auc=TRUE)
```


2). Train Test Split.
```{r}
set.seed(20)
sample_siz = floor(0.75*nrow(clean))  
train_index = sample(seq_len(nrow(clean)),size = sample_siz)
train=clean[train_index,] 
test=clean[-train_index,] 
mylogit_train<-glm(Churn~ gender+SeniorCitizen+Partner+Dependents+tenure+PhoneService+MultipleLines+OnlineSecurity+OnlineBackup+
                   DeviceProtection+TechSupport+StreamingTV+StreamingMovies+PaperlessBilling+
                   MonthlyCharges+EC+MC+BT+mtm+oy+DSL+StreamingTV:StreamingMovies,data=train,family=binomial(link="logit"))
summary(mylogit_train) 
preddata_test_lr<-with(test,data.frame(customerID,gender,SeniorCitizen,Partner,Dependents,tenure,PhoneService,MultipleLines,OnlineSecurity,OnlineBackup,DeviceProtection,TechSupport,StreamingTV, StreamingMovies, PaperlessBilling, MonthlyCharges, TotalCharges, Churn, EC,MC,BT,CC,mtm,oy,ty,DSL,FO))
probdefault_test_lr<-predict(mylogit_train,newdata=preddata_test_lr,type="response")
preddefault_test_lr<-ifelse(probdefault_test_lr > 0.5, 1,0) #at what level should we say prob(default)=1
confusionMatrix(data = as.factor(preddefault_test_lr),reference = as.factor(test$Churn),positive = "1")
library(pROC)
ROC_lr<- roc(test$Churn, probdefault_test_lr)
ROC_lr_auc <- auc(ROC_lr)
plot(ROC_lr, col = "green", main = "ROC For Logistic Regression")
paste("Accuracy % of logistic regression: ", mean(test$Churn == preddefault_test_lr))
paste("Area under curve of logistic regression: ", ROC_lr_auc)
roc(test$Churn,probdefault_test_lr, plot=TRUE, legacy.axes=TRUE, percent=TRUE, xlab="FP Rate", ylab="TP Rate",print.auc=TRUE)
```
3).K-Fold Cross Validation for Logistic Regression.
```{r}
set.seed(20)
cv.error.10=rep(0 ,10)
for (i in 1:10){
  glm.fit=glm(Churn~ gender+SeniorCitizen+Partner+Dependents+tenure+PhoneService+MultipleLines+OnlineSecurity+OnlineBackup+
                   DeviceProtection+TechSupport+StreamingTV+StreamingMovies+PaperlessBilling+
                   MonthlyCharges+EC+MC+BT+mtm+oy+DSL+StreamingTV:StreamingMovies,data=clean,family=binomial(link="logit"))
  cv.error.10[i]=cv.glm(clean,glm.fit,K=10)$delta[1]
}
cv.error.10
```

3). Interpret the Logistic Regression Model.
```{r}
oddsr=round(exp(cbind(OddsRatio=coef(churn_logit),confint(churn_logit))),4)
oddsr
```




2. Random Forest.
```{r}
library(randomForest)
rf_model <- randomForest(as.factor(Churn) ~gender+SeniorCitizen+Partner+Dependents+tenure+PhoneService+MultipleLines+OnlineSecurity+OnlineBackup+
                   DeviceProtection+TechSupport+StreamingTV+StreamingMovies+PaperlessBilling+
                   MonthlyCharges+EC+MC+BT+mtm+oy+DSL+StreamingTV:StreamingMovies, data = train)
rf_prediction <- predict(rf_model, test, type = "prob")
preddefault_test_rf<-ifelse(rf_prediction[,2]> 0.5, 1,0) #at what level should we say prob(default)=1
library(pROC)
ROC_rf <- roc(test$Churn, rf_prediction[,2])
ROC_rf_auc <- auc(ROC_rf)
plot(ROC_rf, col = "green", main = "ROC For Random Forest (GREEN) vs Logistic Regression (RED)")
lines(ROC_lr, col = "red")
paste("Accuracy % of random forest: ", mean(test$Churn == preddefault_test_rf))
paste("Accuracy % of logistic regression: ",mean(test$Churn == preddefault_test_lr))
paste("Area under curve of random forest: ", ROC_rf_auc)
paste("Area under curve of logistic regression: ", ROC_lr_auc)
```
3. CLV Based on Logistic Regression.
1) CLV.
```{r}
clean$customer_life<-(1/clean$probchurn)
clean$retention_rate<-(1-clean$probchurn)
clean$margin<-clean$MonthlyCharges*0.17
clv_function<-function(x,y,k) {
sum=0
n = 1
while (n <= round(x,digits =0)) {
num<-k*(y*1/(1+0.08/12))^n
sum<-sum+num
n = n + 1
return(sum)
}
}
result <- data.frame(matrix(nrow = nrow(clean), ncol = 1))
colnames(result) <- c("CLV")
for(i in 1:7032) {
 result[i,1]<-clv_function(clean[i,29],clean[i,30],clean[i,31])
}
clean<-cbind(clean,result)
```

2). Churn Probability Reduced by Adopting Interventions.
```{r}
most_at_risk<-subset(clean, clean$probchurn>0.5)
negative_synergy<-subset(most_at_risk,most_at_risk$StreamingMovies==1 & most_at_risk$StreamingTV==1)
paperless_billing<-subset(most_at_risk,most_at_risk$PaperlessBilling==1)
log_synergy<-1/(1+exp(0.35))
log_auto<-1/(1+exp(0.34))
negative_synergy$newchurn<-negative_synergy$probchurn-log_synergy
paperless_billing$newchurn<-paperless_billing$probchurn-log_auto
```
3). Business Value Added by Adopting Interventions.

```{r}
new<-rbind(negative_synergy,paperless_billing)
nrow(new)
new$newret<-1-new$newchurn
result_new <- data.frame(matrix(nrow = nrow(new), ncol = 1))
colnames(result_new) <- "New CLV"
for(i in 1:1810) {
 result_new[i,1]<-clv_function(new[i,29],new[i,34],new[i,31])
}
sum(result_new-new$CLV)
```


